---
title: "Initializing a dashboard"
author: "Richard White"
date: "2018-10-26"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Bounded context for the dashboards project

The `fhi` package contains a number of functions that span the [dashboards](https://folkehelseinstituttet.github.io/dashboards/) project.

As mentioned in the [umbrella documentation](https://folkehelseinstituttet.github.io/dashboards/integrating-the-r-package-into-the-physical-system.html#bounded-context), we expect that for the automated analysis `ANALYSIS`, there is an R package called `ANALYSIS` and the following folder structure exists on the system:

```{}
/MASTERFOLDER/data_raw/
  |-- ANALYSIS/
/MASTERFOLDER/data_clean/
  |-- ANALYSIS/
/MASTERFOLDER/data_app/
  |-- ANALYSIS/
/MASTERFOLDER/results/
  |-- ANALYSIS/
/MASTERFOLDER/src/
  |-- ANALYSIS/
     |-- 0_run.sh
     |-- RunProcess.R
     |-- RunTest.R
```

It is important to note that we generally do not use `MASTERFOLDER` in production settings.

## fhi::DashboardInitialiseOpinionated

[fhi::DashboardInitialiseOpinionated](../reference/DashboardInitialiseOpinionated.html) is always the first function called in a [RunProcess.R](https://folkehelseinstituttet.github.io/dashboards/integrating-the-r-package-into-the-physical-system.html#runprocess.r) file. Its main purpose is to properly initialise the environment `fhi::PROJ`.

```{r}
for(i in names(fhi::PROJ)){
  print(sprintf("%s=%s",i,fhi::PROJ[[i]]))
}
```

`fhi::PROJ$PRODUCTION_NAME` contains a list of all the computer names that are consided to be production machines.

`fhi::PROJ$COMPUTER_NAME` is this current computer's name. It is obtained from the file `/tmp/computer`.

`fhi::PROJ$IS_PRODUCTION` is used in the getter function [fhi::DashboardIsProduction](../reference/DashboardIsProduction.html). This is primarily used to choose the appropriate mailing lists (i.e. production computer sends emails to the customers, test/development computers send emails to the developers).

```{r}
fhi::DashboardIsProduction()
```

`fhi::PROJ$IS_DEV` is used in the getter function [fhi::DashboardIsDev](../reference/DashboardIsDev.html). It is flagged to `TRUE` if the script is called from within RStudio (i.e. a development environment). All automated analyses check for existing results before running (and exit if existing results are found). This getter function is generally used decide if we should delete existing results (i.e. if we are developing code then we don't care if there are existing results, we just want to see what the new version of the results looks like).

```{r}
fhi::DashboardIsDev()
```

`fhi::PROJ$IS_INITIALISED` is used in the getter function [fhi::DashboardIsInitialised](../reference/DashboardIsInitialised.html). If the project is initialised, then you know that you are working in the integrated umbrella [dashboards](https://folkehelseinstituttet.github.io/dashboards/) environment. This function is not used very often.

```{r}
fhi::DashboardIsInitialised()
```

Here we now create the necessary file structure:
```{r}
# Create an empty package
pkg <- file.path(tempdir(check=TRUE),"ANALYSIS")
usethis::create_package(pkg,quiet=F)

# Create the data/results/src folders
tmpdir <- tempdir(check=TRUE)
dir.create(file.path(tmpdir,"data_raw"))
dir.create(file.path(tmpdir,"data_clean"))
dir.create(file.path(tmpdir,"data_app"))
dir.create(file.path(tmpdir,"results"))
dir.create(file.path(tmpdir,"src"))

# Create the `ANALYSIS` specific folders inside
dir.create(file.path(tmpdir,"data_raw","ANALYSIS"))
dir.create(file.path(tmpdir,"data_clean","ANALYSIS"))
dir.create(file.path(tmpdir,"data_app","ANALYSIS"))
dir.create(file.path(tmpdir,"results","ANALYSIS"))
dir.create(file.path(tmpdir,"src","ANALYSIS"))

# Initialise
fhi::DashboardInitialiseOpinionated("ANALYSIS",STUB=tmpdir, PACKAGE_DIR=pkg, FORCE_DEV_PACKAGE_LOAD=TRUE)

# Lets see how `fhi::PROJ` has changed:
for(i in names(fhi::PROJ)){
  print(sprintf("%s=%s",i,fhi::PROJ[[i]]))
}
```

We can see that we have a few new extra variables:

`fhi::PROJ$SRC` is the location of the `src` directory.

`fhi::PROJ$NAME` is the name of the automated analysis.

`fhi::PROJ$STUB` is the master folder containing all of the data folders.

We can also see how the getter functions have changed:

```{r}
# Hopefully not!
fhi::DashboardIsProduction()

# This one is a little special, because we used the flag `FORCE_DEV_PACKAGE_LOAD=TRUE`
fhi::DashboardIsDev()

# Obvious
fhi::DashboardIsInitialised()
```

## fhi::DashboardMsg

According to the [code style guidelines](https://folkehelseinstituttet.github.io/dashboards/contributing.html#code-style) we do not use `print`. We instead use `message`, `warning`, and `stop`. 

[fhi::DashboardMsg](../reference/DashboardMsg.html) is a stylised version of `message`, `warning`, and `stop`. It prints the requested message with a timestamp and a traceback of system calls. This is useful in log files.

```{r}
MyFirstFunction <- function(d){ fhi::DashboardMsg("Important message!")}
MySecondFunction <- function(a=2){ MyFirstFunction(d=4) }
MyThirdFunction <- function(){ MySecondFunction() }
MyThirdFunction()
```



